---
title: "Detaild Lecture Outline and Additional Resources"
published-title: "Date"
description: "Resources associated with each section of the lecture."
date: "2025-07-01"
self-contained: true
engine: knitr
---

## Detailed outline and resources

Here is the outline of the lecture, along with links to additional resources on each topic.

### Introduction

### Usefulness and importance
  
- Explore and explain
  - [Why looking at data?](https://socviz.co/lookatdata.html#why-look-at-data)
  - [Existing tools for exploratory data analysis in R ](https://cosimameyer.com/post/exploratory-data-analysis-in-r/) 
- Deceptive visualizations
  - [Defense against dishonest charts](https://flowingdata.com/projects/dishonest-charts/)
  
### Key data viz principles

- Perception and color
  - More on [Gestalt principles](https://medium.muz.li/gestalt-principles-in-ui-design-6b75a41e9965) (plus [a research article](https://www.nature.com/articles/nmeth1110-863))
  - [How to find and create good color palettes](https://www.datawrapper.de/blog/beautifulcolors) on 
- Data-to-ink ratio
  - [A critique of the data-to-ink ratio](https://www.frank.computer/blog/2025/04/data-to-ink.html)
- Aesthetics
  - [Reasons to make beautiful graphs](https://medium.com/accurat-in-sight/beautiful-reasons-c1c6926ab7d7) on 
  - [Credibility and typography](https://practicaltypography.com/why-does-typography-matter.html)
  - [In defense of simple charts](https://www.datawrapper.de/blog/in-defense-of-simple-charts)
  
### Building a graph

- Graph galeries
  - [Data Viz Project](https://datavizproject.com/)
  - [Flowing Data - Chart type](https://flowingdata.com/chart-types/)
  - [Dataviz Inspiration](https://www.dataviz-inspiration.com/)
  - [R graph gallery](https://r-graph-gallery.com/)
- [What questions to ask when creating charts](https://www.datawrapper.de/blog/better-charts)
- Decision trees for a graph type
  - [Financial Times tree](https://github.com/Financial-Times/chart-doctor/tree/main/visual-vocabulary)
  - [Data viz catalogue](https://datavizcatalogue.com/search.html)
  - [Datawrapper guide](https://www.datawrapper.de/blog/chart-types-guide)
  - [Data to viz graph](https://www.data-to-viz.com/)
- Concrete recommendations
  - [For color](https://www.datawrapper.de/blog/colors)
  - [For text](https://www.datawrapper.de/blog/text-in-data-visualizations)
- Specific do's and don'ts
  - [Statistics oriented](https://github.com/cxli233/FriendsDontLetFriends)
  - [A collection of dataviz caveats](https://www.data-to-viz.com/caveats.html)
  - [Sometimes it's ok to break the rules](https://medium.economist.com/why-you-sometimes-need-to-break-the-rules-in-data-viz-4d8ece284919)
  
### Data viz for research in economics

- When do we use graphs in econ? 
- Specificities of viz in econ
  - [Avoid overplotting](https://www.data-to-viz.com/caveat/overplotting.html)
  - [Visualize regression output](https://modelsummary.com/)
  - [Visualize regression output with distributions](https://mjskay.github.io/ggdist/articles/freq-uncertainty-vis.html?q=estimate#point-estimates)

### Main take-away messages
  
## Slides

```{r render_slides_pdf}
#| eval: false
#| echo: false

renderthis::to_pdf(
  from = "docs/content/slides/slides_data_viz_summer.html", 
  to = "content/slides/slides_data_viz_summer.pdf"
)

renderthis::to_pdf(
  from = "docs/content/slides/slides_data_viz_summer.html", 
  to = "docs/content/slides/slides_data_viz_summer.pdf"
)
```


`r fontawesome::fa("file-powerpoint")` [Open slides in html](../slides/slides_data_viz_summer.html)

`r fontawesome::fa("file-pdf")` [Open slides in PDF](../slides/slides_data_viz_summer.pdf)

```{r out.width='100%'}
#| echo: false

knitr::include_url("../slides/slides_data_viz_summer.html")
```







